Mendelian randomization for causal inference in Genome-wide association studies

### 2022-02-19 mr-review.Rmd
deleted "and one outcome" from section header

## Statistical models and methods for MR with one instrument and one outcome

@@

```{r, dag2, fig.cap = "Scenario where the genetic variant G affects exposure X, which in turn affects Y. Unobserved confounder U affects both X and Y."}
d1 <- dagitty('dag {
bb="0,0,1,1"
G [pos="0.0,0.0"]
U [pos="0.75,0.5"]
X [exposure, pos="0.5,0.0"]
Y [outcome, pos="1.0,0.0"]
G -> X
U -> X
U -> Y
X -> Y
}'
)
plot(d1)

@@

The second type of horizontal pleiotropy, from above, is sometimes called "correlated horizontal pleiotropy". Correlated horizontal pleiotropy occurs when

>>>>

## Statistical models and methods for MR with one instrument

@@

```{r, dag2, fig.cap = "Scenario where the genetic variant G affects exposure X, which affects Y. Unobserved confounder U affects both X and Y."}
d1 <- dagitty('dag {
bb="0,0,1,1"
G [pos="0.0,0.0"]
U [pos="0.75,0.5"]
X [exposure, pos="0.5,0.0"]
Y [outcome, pos="1.0,0.0"]
G -> X
U -> X
U -> Y
X -> Y
}'
)
plot(d1)

@@

The second type of horizontal pleiotropy, from above, is sometimes called 
"correlated horizontal pleiotropy". Correlated horizontal pleiotropy occurs 
when a SNP affects both the exposure and a variable that confounds the 
relationship between exposure and outcome (Figure \@ref(fig:dag3)).

```{r, dag3, fig.cap = "Correlated horizontal pleiotropy occurs when the genetic variant G affects exposure X, which in turn affects Y, and G affects U, which in turn affects X and Y independently."}
d1 <- dagitty('dag {
bb="0,0,1,1"
G [pos="0.0,0.0"]
U [pos="0.75,0.5"]
X [exposure, pos="0.5,0.0"]
Y [outcome, pos="1.0,0.0"]
G -> X
G -> U
U -> X
U -> Y
X -> Y
}'
)
plot(d1)
